\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\titleformat{\section}{\large\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    \LARGE \textbf{Marcus Raymond Cummings} \\
    \normalsize 15 Lübbenner Straße, 10997 Berlin, Germany \\
    \faEnvelope \hspace{0.5mm} \href{mailto:youremail@example.com}{email@example.com} \quad
    \faGithub \hspace{0.5mm} \href{https://github.com/yourusername}{github.com} \quad
    \faGlobe \hspace{0.5mm} \href{https://yourportfolio.github.io}{portfolio.github.io}
\end{center}

\section*{Personal Profile}
A highly driven and adaptable software engineering professional with cross-functional expertise in network engineering, programming, event organization, and youth development. Demonstrates exceptional problem-solving, communication, and leadership skills across both technical and community-oriented environments. Passionate about using technology to solve real-world problems and deliver measurable impact.

\section*{Work Experience}

\textbf{Network Engineer} \hfill \textit{Esscon Services} \\
\textit{Berlin, Germany} \hfill \textit{June 2023 – May 2024}
\begin{itemize}[leftmargin=*]
    \item Monitored and maintained high-performance networks, ensuring 99.9\% uptime.
    \item Collaborated with cross-functional teams to implement robust network upgrades.
    \item Strengthened cybersecurity posture through proactive threat mitigation protocols.
    \item Provided user-friendly technical support and reduced downtime through clear communication.
\end{itemize}

\textbf{Youth Coordinator} \hfill \textit{Action for Children and Youth Agency} \\
\textit{Accra, Ghana} \hfill \textit{June 2019 – August 2020}
\begin{itemize}[leftmargin=*]
    \item Organized and delivered workshops to over 100+ youths, improving life choices and reducing risk-taking behavior.
    \item Partnered with NGOs to expand youth program reach by 30\%.
    \item Mentored participants, enhancing confidence and community engagement.
    \item Led volunteer recruitment and training, improving program delivery and impact.
\end{itemize}

\textbf{Event Organizer} \hfill \textit{Manchester International Football Academy} \\
\textit{Manchester, UK} \hfill \textit{September 2015 – 2017}
\begin{itemize}[leftmargin=*]
    \item Orchestrated football tournaments fostering local youth participation and inclusivity.
    \item Secured sponsor funding and community support through stakeholder engagement.
    \item Boosted visibility through innovative campaigns combining social media and local outreach.
    \item Conducted post-event analytics and reporting to guide future events.
\end{itemize}

\section*{Education}

\textbf{BEng Software Engineering (Ongoing)} \hfill \textit{GISMA University of Applied Sciences} \\
\textit{Germany} \hfill \textit{2024 – Present}

\textbf{Diploma in Software Engineering} \hfill \textit{BlueCrest College} \\
\textit{Accra, Ghana}
\begin{itemize}[leftmargin=*]
    \item Gained hands-on proficiency in Python, Java, SQL, HTML, and full-stack development.
    \item Built scalable web and desktop applications using agile development practices.
\end{itemize}

\textbf{Level 1 Award in Coaching Football} \hfill \textit{Manchester International Football Academy}

\section*{Core Skills}

\textbf{Technical Skills:}
Network Optimization, Cybersecurity, Software Development, Full-Stack Programming (Python, Java, HTML, SQL), System Troubleshooting

\textbf{Project Management:}
Agile Methodology, Task Prioritization, Team Leadership, Event Planning

\textbf{Communication:}
Public Speaking, Report Writing, Training \& Mentorship, Stakeholder Engagement

\textbf{Soft Skills:}
Adaptability, Problem-Solving, Cross-cultural Teamwork, Creativity

\section*{Projects \& Portfolio}
\begin{itemize}[leftmargin=*]
    \item \textbf{Portfolio Website:} \href{https://yourportfolio.github.io}{yourportfolio.github.io} – Responsive personal website built using HTML, CSS, and GitHub Pages to showcase projects and resume.
    \item \textbf{GitHub Repository:} \href{https://github.com/yourusername/portfolio}{github.com/yourusername/portfolio}
\end{itemize}

\end{document}
